Detector_Validation

### 2021-04-16 analysis/_old_analysis/analysis_bb_fulldataset.Rmd
reorg analysis scripts -- port outdated/draft scripts to "old" folder

### Load preprocessed bb's for all kids
```{r}
load(file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')

@@

```{r}
hands_by_size_by_frame <- bb_all %>%
  filter(label=="hand") %>%
  group_by(vid_name, frame, age_days, child_id) %>%
  summarize(num_hands = sum(label=="hand"), avg_area = mean(area), avg_x = mean(center_x), avg_y = mean(center_y))

>>>>

### Load preprocessed bb's for all kids
```{r}
load(file = '../data/preprocessed_data/all_bounding_boxes_three_kids_preprocessed.RData')
```

### Randomly sample some subset of the data
```{r}
num_to_sample = .1*length(bb_all_three$frame)
bb_all_three_sample <- bb_all_three %>%
  sample_frac(.1)
```

```{r}
save(file = '../data/preprocessed_data/all_bounding_boxes_three_kids_preprocessed_small_sample.RData', bb_all_three_sample)
```

bb_all <- bb_all_three_sample
```

```{R}
ggplot(bb_all_three_sample) +
  geom_histogram(aes(x=height)) +
  facet_wrap(~child_id)

@@

```{r}
hands <- bb_all %>%
  filter(label=='hand')

```{r}
hands_by_size_by_frame <- hands %>%
  group_by(vid_name, frame, age_days, child_id) %>%
  summarize(num_hands = n(), avg_area = mean(height*width), avg_x = mean(center_x), avg_y = mean(center_y))

### 2021-04-16 analysis/_old_analysis/analysis_bb_fulldataset_2.Rmd
reorg analysis scripts -- port outdated/draft scripts to "old" folder

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
theme_set(theme_few())
```

>>>>

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
library(here)
theme_set(theme_few())
```

### 2021-04-16 analysis/_old_analysis/detector_validation 2.Rmd
reorg analysis scripts -- port outdated/draft scripts to "old" folder

### Instead load in detections and ketan's gold set annotations from preprocessed Rdata files
```{r}
load('../data/openpose_detections.RData')
load('../data/ketan_gold_sample.RData')
```

@@

meta=read.csv(metadata_file) %>%
  mutate(vid_name_short = str_split_fixed(File.Name,'.AVI',2)[,1]) %>%
  rowwise() %>%
  mutate(count_locations = length(str_split(Location,',')[[1]]))

# location_data <- meta %>%
#   filter(count_locations==1) %>%

@@

# weird_gs_frames <- m_seg %>%
#   mutate(weird = (label=='Child face')) %>%
#   filter(weird==TRUE)

>>>>

### Instead load in detections and ketan's gold set annotations from preprocessed Rdata files
```{r}
# load('../data/openpose_detections.RData')
load('../data/ketan_gold_sample.RData')
```

@@

meta=read.csv(metadata_file) %>%
  mutate(vid_name_short = str_split_fixed(File.Name,'.AVI',2)[,1]) %>%
  rowwise() %>%
  mutate(count_locations = length(str_split(Location,',')[[1]]))
```

@@

### 2021-04-16 analysis/_old_analysis/detector_validation.Rmd
reorg analysis scripts -- port outdated/draft scripts to "old" folder

### Instead load in detections and ketan's gold set annotations from preprocessed Rdata files
```{r}
# load('../data/openpose_detections.RData')
load('../data/ketan_gold_sample.RData')
```

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
right_side_up_file = "../data/video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

# get INCORRECT videos
flipped_videos <- right_side_up %>%
  filter(right_side_up==1)
```

### Get metadata from file
```{r}
metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"

@@

### Read in turk anotation data  and merge
#### First read in hand/face present only here, ~4K images
```{r}
turk_annotations = "../data/turk_annotations_dec5.csv" # 20 turkers who did ~250 frames each
gold_set = read.csv(turk_annotations)

@@

### Import hand segmentations
```{r eval=FALSE}
turk_annotations_seg = "../data/turk_segmentations_hands_only_processed.csv" 
g_seg = read.csv(turk_annotations_seg)

@@

prf_by_age_hands <- d %>%
  mutate(hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose)) %>%
  group_by(age_day_bin, child_id) %>%
  do(return_prf(.$hand_eval_ketan))
```

>>>>

### Instead load in detections and ketan's gold set annotations from preprocessed Rdata files
```{r}
## 25K annotations are only on S/A
load('../data/raw_data/openpose_detections_SA.RData')
load('../data/raw_data/ketan_gold_sample.RData')
```

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
right_side_up_file = "../data/raw_data/SAYCAM_allocentric_videos.csv"
right_side_up =read.csv(right_side_up_file)

# get INCORRECT videos
flipped_videos <- right_side_up %>%
  filter(allocentric==1)
```

### Get metadata from file
```{r}
metadata_file = "../data/raw_data/Metadata_SAYcam-2019-12-0922_54_28.csv"

@@

### Read in turk anotation data  and merge
#### First read in hand/face present only here, ~4K images
```{r}
turk_annotations = "../data/turk_data/turk_annotations_dec5.csv" # 20 turkers who did ~250 frames each
gold_set = read.csv(turk_annotations)

@@

### Import hand segmentations
```{r eval=FALSE}
turk_annotations_seg = "../data/turk_data/turk_segmentations_hands_only_processed.csv" 
g_seg = read.csv(turk_annotations_seg)

@@

prf_by_age_hands <- d %>%
  mutate(hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose)) %>%
  group_by(age_day_bin, child_id) %>%
  do(return_prf(.$hand_eval_ketan))

##
prf_by_age_hands_both_kids <- d %>%
  mutate(hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose)) %>%
  group_by(age_day_bin) %>%
  do(return_prf(.$hand_eval_ketan))
```

```{r}
prf_by_child_hands <- d %>%
  mutate(hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose)) %>%
  group_by(vid_name_short) %>%
  do(return_prf(.$hand_eval_ketan))

prf_by_child_faces <- d %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose)) %>%
  group_by(child_id) %>%
  do(return_prf(.$face_eval_ketan))

# not that useful since vids are so long for A

# face_prf_by_vid <- d %>%
#   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose)) %>%
#   group_by(vid_name_short, Databrary.Link) %>%
#   do(return_prf(.$face_eval_ketan)) 
# 
# low_p_vids <-  face_prf_by_vid %>%
#   filter(p<.2) %>%
#   filter(num_detect > 40)
```

```{r}
ggplot(prf_by_age_hands_both_kids, aes(x=age_day_bin, y=p, col=age_day_bin, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth()  +
  ylab('F-score - Face detection')
